---
title: "Practical 2: T-tests and Correlations"
subtitle: "Introduction to R and Rstudio"
output: html_notebook
---

#Introduction

This is assignment copy for Practical 2, the solutions copy is names `Practical2Solutions.Rmd`.
For queries, please email `shane.galvin@ucc.ie`.

This data is a portion of a larger data set available from:
https://drive.google.com/file/d/0Bz-rhZ21ShvOdW1wV0pmUTJSSk0/view

The parent site is:
https://sites.trinity.edu/osl/data-sets-and-activities/t-test-activities

Data originally published as:

Does Music Convey Social Information to Infants?

Original article: Mehr, S. A., Song. L. A., & Spelke, E. S. (2016). For 5-month-old infants, melodies are social. Psychological Science, 27, 486-501.

available at:
http://journals.sagepub.com/stoken/default+domain/d5HcBHg85XamSXGdYqYN/full

## Aim:
To compare
This study compared infant gaze a
"First, the infant viewed side-by-side high-definition video recordings of the two unfamiliar individuals, smiling with direct gaze at the infant, for 16 s (baseline trial). Then, the infant viewed, in turn, one 22-s video of each of the two individuals singing one of the two songs while continuing to look and smile at the infant. 
Finally, the infant viewed a silent 16-s test trial that was identical to the baseline trial. A looming object with an attractive sound effect brought the infant’s eyes to the center of the screen before the baseline and test trials"

"At test, however, the infants selectively attended to the now-silent singer of the song with the familiar melody; the proportion of time during which they looked toward ... greater than the proportion at baseline
(difference in proportion of looking: M = .072, SD = .169,
95% CI = [.011, .133]), t(31) = 2.42, p = .022, d = 0.43" (p4 in.pdf version)

This practical will use proportion of gaze timebaseline data with final condition of the silent 16-s test.

IV: Proportion of Gaze Time
DV: Baseline (Control), Experimental Condition (Silent Singers)
The aims of this practical are as follows:

- 0 Read in the Data File
- 1 Summarise Data by group|total Means and StDec in particular
- 2 Visualise Data by group|total Histograms and a boxplot
- 3 Perform a REPEATED MEASURES t-test using the `t.test()` function
- 4 Calculate the appropriate effect size measure with the `effsize` package
- 5 Calculate the POST-HOC Power with the `pwr` package

You may looad and use the following packages:
`psych`, `summarytools`,`pwr` and `effsize`
Make liberal use of the helper function, either through pressing F1 during autocomplete, or using`?t.test` or any other function.
You can also compile this into a rendered HTMLbook by clicking the preview button on the task bar above this script.
```{r}

```

#Practical

##0 Read the data file `"Practical2Data.csv"` into an object names p2d, then print out the dataframe
```{r}
```

##1 Summarise data 
```{r}
```

Note the Means and Standard Deviations for each group and the total

##2 Visualise Data
```{r}
```

comment on the distributions and histograms:


##3 Perform F test
```{r}
```
Note if the variances are equal


##4 Normality

Use the Shapiro-Wilks test for all the Proportion data
```{r}

```


use the Shapiro-Wilks test on the Proportion data for the Baseline condition
```{r}
```


Use the Shapiro-Wilks test on the Proportion data for the Experimental condition
```{r}
```


# Repeated samples t.test

inside the t.test function you will have to use the `paired=TRUE` argument for the t test to run 
```{r}
```

## Effect size
Now Calulate the effect size using the `effsize` package
```{r}
```

## Post-hoc Power
```{r}
```

